An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-24 paper/paper.tex
Paper: write conclusion section for results of filesize vs numfiles test scenario

\subsection{Data Recovery Speed from Nodes' Perspective}

@@

\subsection{Entities Backing Up a 1 GB File}

@@

We have seen BitTorrent Sync handle 
% 1. how well does btsync handle large number backups? how well will it scale?
% 2. measure performance of bittorrent against diff file sizes
% 3. bittorrent faster than direct download?

>>>>

\subsection{Data Recovery Speed from Nodes' Perspective} \label{subsec:DataRecoverySpeedfromNodesPerspective}

@@

\subsection{Entities Backing Up a 1 GB File} \label{subsec:EntitiesBackingUpa1GBFile}

@@

% TODO - do we actually test this now that we aren't doing the 1000x1mb test? may need to remove goal from methodology.
% 1. how well does btsync handle large number backups? how well will it scale?

Section \ref{subsec:DataRecoverySpeedfromPeersPerspective} compared how our system performs when recovering many small files versus few large files. We concluded that there is a large performance gain by recovering fewer, larger files, but the returns diminish between files of size 100 MB and 1 GB.

Section \ref{subsec:DataRecoverySpeedfromNodesPerspective} verified our hypothesis that our system would recover data faster than an equivalent one using a direct download data transfer protocol. Our data estimates that the speed increase could be upwards of 200\%.

Section \ref{subsec:EntitiesBackingUpa1GBFile} showed that our system lessens the Peer's load of backing up a file by distributing the task to the nodes as well. This has the side effect of speeding up the backup process, because nodes upload the data they have at a given time to each other, better utilizing their download bandwidth.
